Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-30 paper-filmat.tex
Be more modest (in response to review)
typo

\section{The \effective topos, a convenient home for computability theory}
\label{sect:effective-topos}

@@

A basic observation in computability theory is that there are computational tasks
which are not solvable even for these idealized Turing machines. The paramount
example is the \emph{halting problem}: Given a Turing machine~$M$, determine
whether~$M$ terminates (comes to a stop after having carried out finitely
many computational steps) or not.

@@

XXX: Kleene-Vesley topos?

>>>>

\section{The \effective topos, a universe shaped by computability}
\label{sect:effective-topos}

@@

A basic observation in computability theory is that there are computational tasks
which are not solvable even for these idealized Turing machines. The premier
example is the \emph{halting problem}: Given a Turing machine~$M$, determine
whether~$M$ terminates (comes to a stop after having carried out finitely
many computational steps) or not.

@@

FUTURE: Kleene-Vesley topos
